McNemar's test

### 2025-05-09 text/23/mcnemar-test.Rmd
Removed brackets from generic code chunks

```{r}
a <- 833; b <- 125; c <- 2; d <- 160
n <- a + b + c + d
r1 <- round(100*(a+b)/n)
c1 <- round(100*(a+c)/n)
T <- round((b-c)^2/(b+c), 1)
```

@@

In the survey about heaven and hell, b=`r b` and c=`r c`. The test statistic is

-   $T = \frac{(125-2)^2}{127} = `r T`$

If you want to enter this data into a program like SPSS, you can't type it as you see it.

@@

It would be nice if you could do this, but it doesn't work for a variety of reasons. You need to put each count on a separate row. Specify the belief in heaven (yes/no) as the first column and belief in hell (yes/no) as the second column. The count for each combination goes in the third column.

```{}
heaven,hell,count
1,1,833
1,2,125
2,1,2
2,2,160
```

Make sure that you designate count as a weight before starting your analysis. Here is what the output looks like in SPSS

![](http://www.pmean.com/new-images/23/mcnemar-test-02.png)

Here is what it looks like in R

```{r}
mcnemar.test(matrix(c(833, 125, 2, 160), nrow=2), correct=FALSE)
```

>>>>

```{r, echo=FALSE}
a <- 833; b <- 125; c <- 2; d <- 160
n <- a + b + c + d
r1 <- round(100*(a+b)/n)
c1 <- round(100*(a+c)/n)
T <- round((b-c)^2/(b+c), 1)
```

@@

In the survey about heaven and hell, b=125 and c=2. The test statistic is

-   $T = \frac{(125-2)^2}{127} = 119.1$

If you want to enter this data into a program like SPSS or R, you can't type it as you see it.

@@

It would be nice if you could do this, but it doesn't work for a variety of reasons. You need to put each count on a separate row. Specify the belief in heaven (yes/no) as the first column and belief in hell (yes/no) as the second column. Notice how the order is staggered to allow all four combinations to appear. The count for each combination goes in the third column.

```{}
heaven,hell,count
"yes","yes",833
"yes","no",125
"no","yes",2
"no","no",160
```

Make sure that you designate count as a weight before starting your analysis. In SPSS, select

-   Analyze | Nonparametric Tests | Legacy Dialogs | 2 Related Samples

from the menu.

In R, use the

-   mcnemar.test

function.
